Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2018-12-16 paper.tex
Fix missing cross-ref links
Changes adapted from Elton 20181212

\usepackage{xr}
\externaldocument[SI-]{SI}

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\date{}
\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
% \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
\begin{document}

@@

{\bfseries Dielectric constant, which defines the polarization of the
  media, is a key quantity in condensed matter. Here we show that
  despite its fundamental transcendence, the dielectric constant does
  not define unequivocally the dielectric properties of a
  two-dimensional (2D) material. We found instead that the dielectric
  polarizability correctly captures the dielectric nature of a 2D
  material which is strongly dependent on the long-range
  electron-electron interaction.  We reveal a long-sought universal
  framework where electronic, geometrical and dielectric properties
  are intrinsically correlated through the polarizability opening the
  door to probe quantities yet not directly measurable, e.g. thickness
  of an atom.  By using this framework, we unify the concept of
  dielectric properties in any material dimension through a dielectric
  anisotropy index which defines the degree of controllability of the
  dielectric features of a compound. A universal boundary line
  separates the 3D and 2D behaviors where materials likely to have
  similar properties as layered materials collapsed onto.  }

The central place of dielectric properties, especially the static
dielectric constant in material research
\cite{Dressel_2001_electrodynamics} drives the pursuit for a unified
model between the electronic and dielectric properties of materials.
% In fact, some pioneering work\cite{Moss_1950_relation} discovered
% relations between the dielectric constant $\varepsilon$ and other
% physical properties, in particular the band gap $E_{\mathrm{g}}$ of
% bulk semiconductors.
In fact, some pioneer
work\cite{Moss_1950_relation,Moss_1985_n_Eg,Ravindra_1979_eps_Eg,Ravindra_2007_Eg_rev}
proposed the empirical model between the energy bandgap
$E_{\mathrm{g}}$ and dielectric constant $\varepsilon$ of bulk
semiconductors, such as the famous Moss relation
\cite{Moss_1950_relation,Moss_1985_n_Eg}:
\begin{equation}
\label{eq:Moss-relations}
\varepsilon^{2} E_{\mathrm{g}} \approx 95\ \mathrm{eV}
\end{equation}
Despite the minor difference between the empirical formulae proposed,
such general relation  is of high
practical importance for material design and engineering: with the
Moss relationship or other similar models, it is feasible to predict
the dielectric constant (and hence other parameters such as refractive
index, Bohr radius, exciton binding energy, etc.) of a bulk material
from the its bandgap with a reasonable degree of certainty
% The
% existence of such general relationship is also of high practical
% importance: it is generally more straightforward and accurate to
% measure the band gap $E_{\mathrm{g}}$ than the static dielectric
% constant $\varepsilon$ of a bulk material, as the latter is strongly
% dependent on several critical details on the sample measurements, such
% as contamination, disorder, and model interpretation.
While the electronic-dielectric relation for bulk semiconductors is
well-established, it is unknown if such equation still exists in
atomically-thin two-dimensional (2D) materials \cite{Novoselov_2016},
due to (i) the dielectric screening of a 2D material is attenuated and
anisotropic
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012}
and (ii) the static dielectric constant, a quantity associated with
the macroscopic dielectric and optoelectronic properties and commonly
obtained by theoretical calculations of 2D materials
\cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may not well
describe this microscopic and anisotropic dielectric nature of 2D
materials \cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}.
% Therefore, an
% accurate description of the 2D dielectric nature is the prerequisite
% for a 2D Moss-like relation, which could be used to make predictions
% for less-investigated layered crystals and to create materials design
% rules at an accurate level.
Here we show that instead of the dielectric constant,
the 2D polarizabilty correctly captures the dielectric nature
of a 2D material. Based on both theoretical model and first principle
calculations, we reveal the long-sought universal dielectric scaling
relations for 2D materials, depend both on the electronic and
structural information: the in-plane polarizability
$\alpha^{\parallel}_{\mathrm{2D}}$ is inversely proportional to the minimal bandgap
$E_{\mathrm{g}}$, while the out-of-plane polarizability
$\alpha^{\perp}_{\mathrm{2D}}$ is directly related with the thickness
$\delta$ of a 2D materials. We further introduce the concept of
dielectric anisotropy index, to unify 2D and 3D dielectric
property. The proposed universal dielectric scaling relationships of
2D compounds introduce a general pathway for the exploration of their
complex physical and chemical phenomena well beyond the currently
possible applications.
% Based on this
% framework, we further unify the concept of dielectric properties of
% any material dimension, by the dielectric anisotropy index, 
% An analytical quantum-mechanical model is developed
% which give a sound background to the dielectric-scale
% relationships.
% Using such unified relations unify the dielectric
% properties between the 2D materials and their 3D counterparts in a
% natural manner, which ultimately pushes the boundary of the
% understanding of electronic screening in both dimensions.
% The discovery of scaling relationships between dielectric and electronic
% and structural properties in 2D compounds introduces a new and general
% pathway for the exploration of their complex physical and chemical
% phenomena well beyond the currently possible applications.

% \section{Results}
% \label{sec:org752ca78}

\subsection{Dielectric Nature of 2D Materials}
\label{sec:2d}

In pursuit of the Moss-like relation for 2D materials, an accurate
description of their dielectric properties needs to be established,
since the concept of macroscopic dielectric constant is ill-defined
for 2D materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D,Nazarov_2015_2D_3D}. As
shown in Figure \ref{fig-1}a, in routine first principles
calculations, an isolated 2D material is placed in the xy-plane of a

@@

z-direction separating the cell images. The macroscopic dielectric

@@

spatial charge density, $\Omega=AL$ is the volume, $A$ is the xy-plane

@@

majority of 2D semiconductors, the off-diagonal elements of the

@@

\varepsilon_{\mathrm{SL}}^{zz}$. The absence of bonding perpendicular
to the 2D plane confines the induced dipoles along the
\textit{z}-direction: as shown in Figure \ref{fig-1}a and
Supplementary Figure \ref{SI-fig:rho-profile}, the charge density difference
between zero and finite electric fields,
$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ along the
z-axis for an isolated 2H-MoS$_{2}$ layer under
$|\boldsymbol{E}_{z}|=0.01 \mathrm{V\cdot \AA}^{-1}$ only extends to
$\sim{}$12 \AA{} along the z-direction. When $L$ is large enough that
the induced dipoles from periodic images do not interact,
$\boldsymbol{u}$ equals the total dipole moments of a monolayer 2D
materials and independent of the SL size. As a consequence, we can see
from Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, that both

@@

$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on $L$. We show this by

@@

theory (DFT) as functions of $L$ for P$\bar{6}$m2 (2H) transitional
metal dichalcogenides (TMDCs, 2H-MX$_{2}$, where M=Mo, W and X=S, Se,
Te), in the top panels of Figure \ref{fig-1}b and \ref{fig-1}c,
respectively.

@@

% \cite{Hueser_2013_2Dvs3D}.
As a result, the $L$-dependency of $\varepsilon_{\mathrm{SL}}$ makes
it impractical to represent the dielectric nature of a 2D material
both theoretically and experimentally, because the size of vacuum
layer must always be considered. To solve this problem, we need to
find the $L$-independent alternative of
$\varepsilon_{\mathrm{SL}}$. As described before, by multiplying
Eq. \ref{eq:def-eps-2} with $L$ we get the sheet polarization density
of a 2D material $\boldsymbol{\mu}_{\mathrm{2D}}$, such that
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} = \boldsymbol{P}^{p}L =
\boldsymbol{u}^{p}/A$, which is dependent with $L$ due to the invariablity
of $\boldsymbol{u}$ and $A$. Similar to the definition of molecular
polarizability \cite{Israelachvili_2011},
$\boldsymbol{\mu}_{\mathrm{2D}}$ is associated with the 2D
polarizability $\alpha_{\mathrm{2D}}$ through:
$\boldsymbol{\mu}^{p} = \sum_{q} \alpha_{\mathrm{2D}}^{pq}
\boldsymbol{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where
$\boldsymbol{E}_{\mathrm{loc}}$ is the local electric field. In the
in-plane direction, the continuity of electric field gives
$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$
\cite{Markel_2016}. Perpendicular to the 2D plane, the dipole
screening yields
$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}_{\mathrm{2D}}^{\perp}/L$
\cite{Meyer_2001_dipole_slab,T_bik_2004}. Combining with
Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we can relate the 2D polarizabilities,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
% \begin{subequations}
% \begin{eqnarray}
  % \label{eq:alpha-para-def}
  % &\alpha_{\mathrm{2D}}^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\
  % \label{eq:alpha-perp-def}
  % &\alpha_{\mathrm{2D}}^{\perp} &= \varepsilon_{0}\left(1 - {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}}\right)L
% \end{eqnarray}
% \end{subequations}

@@

  \label{eq:alpha-para-def}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0}L}\\
  \label{eq:alpha-perp-def}
  &\varepsilon_{\mathrm{SL}}^{\perp} &= \left(1 - {\displaystyle \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{\mathrm{0}} L}} \right)^{-1}

@@

The bottom panels of Figure \ref{fig-1}b and \ref{fig-1}c show the
of the TMDCs as functions of $L$, calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}. We observe
that both $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ remain almost constant when $L>$15
\AA{}. In addition, as shown Figure \ref{fig-1}d and \ref{fig-1}e,
respectively, the model-predicted
$\varepsilon_{\mathrm{SL}}^{\parallel}-L$ and
$\varepsilon_{\mathrm{SL}}^{\perp}-L$ relations from Eqs.
\ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} nicely reproduce
the trends from Figures \ref{fig-1}b and \ref{fig-1}c. These findings
indicate that the 2D polarizability, instead of the dielectric
constant, is the true descriptor of the dielectric properties of 2D
materials. More discussion about the choice of the 2D polarizability
and comparison with other methods can be find in Supplementary Section
\ref{SI-sec:2D-3D-rescale}.

\subsection{2D Moss-like  Relations}
\label{sec:first-principles}
Based on the 2D polarizabilities, we then investigate the potential
Moss-like relations for 2D materials. By evaluating the expressions
for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ using Random Phase Approximation (RPA)
theory \cite{Adler_1962} with $\mathbf{k} \cdot \mathbf{p}$
treatment\cite{kittel_2005_introduction} (details see Supplementary
Section \ref{SI-ssec:theory-1}), we show that
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
have simple relation with the electronic  and structural information of a 2D
material, respectively:
\begin{subequations}
\begin{eqnarray}
\label{eq:2D-Moss-para}
  &\alpha_{\mathrm{2D}}^{\parallel} &\propto E_{g}^{-1} \\
  \label{eq:2D-Moss-perp}
  &\alpha_{\mathrm{2D}}^{\perp} & \propto \delta
\end{eqnarray}
\end{subequations}
where $E_{\mathrm{g}}$ is the minimal electronic bandgap of the 2D
material, and $\delta$ is its intrinsic
thickness. Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are
the main conclusions of this work.  \todo[inline]{I not sure if we
  need to show the proportional coefficients
  here. $\alpha_{2D}^{\perp}$ is almost certain to be
  $\varepsilon_{0}\delta$, but $\alpha_{\mathrm{2D}}^{\parallel}$ has
  a more complex coefficient.}

>>>>

%\usepackage{xr}
%\externaldocument{SI_v112818}
\usepackage{xr-hyper} 
%\usepackage{zref-xr}
\externaldocument{SI_v120518}

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
%% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\date{}
\title{Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
% \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
\begin{document}

@@

{\bfseries Dielectric constant, which defines the polarization of the media, is a key quantity in condensed matter. It determines several electronic and optoelectronic properties important for a plethora of modern technologies from computer memory to field effect transistors and communication circuits. Moreover, the importance of the dielectric constant in describing electromagnetic interactions through screening plays a critical role in understanding fundamental molecular interactions. Here we show that despite its fundamental transcendence, the dielectric constant does not define unequivocally the dielectric properties of two-dimensional (2D) materials due to the locality of their electrostatic screening. We found instead that the electric polarizability correctly captures the dielectric nature of a 2D material which is united to other physical quantities in an atomically thin layer. We reveal a long-sought universal formalism where electronic, geometrical and dielectric properties are intrinsically correlated through the polarizability opening the door to probe quantities yet not directly measurable including the real covalent thickness of a layer. We unify the concept of dielectric properties in any material dimension finding a global dielectric anisotropy index defining their controllability through dimensionality. 
}

The dielectric constant $\varepsilon$ (also known as the relative permittivity) 
plays a crucial role in bridging various fundamental material
properties, such as bandgaps, optical absorption, and conductivities,   
with elemental interactions, e.g. the electron-electron forces. 
The central place of $\varepsilon$ in physics drives the analysis of several phenomena 
where is common to classify a material accordingly to its ability to screen an electric field $\boldsymbol{E}$ 
in terms of insulators, metals and semiconductors. Such definitions determine a broad range of 
condensed matter physics, as well as in related fields in chemistry and materials science. 
The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
theoretical and experimental techniques of distinct flavors where the probe of the dielectric properties 
is made through an external electric field. 
%
Despite its obvious appeal, however, it is still unknown whether such quantity can determine the 
electronic and dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
%
%
The confined nature of the electrons in such atomically thin space associated with the 
attenuated and anisotropic character of the dielectric screening of 2D crystals 
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
have generated long-standing debates whether the dielectric constant 
may represent their dielectric features or it can be used as an 
additional parameter from the bulk-counterparts. 
%%
%%
We approach to this problem showing 
that the current definition used in layered materials is ill defined as illustrated in Figure \ref{fig-1}.  
From the theoretical point of view, 
an isolated 2D material is placed in the xy-plane of a  %cutting started here! 

@@

z-direction separating the cell images. The static macroscopic dielectric

@@

spatial charge density, $\Omega=AL$ is the volume of the supercell, $A$ is the xy-plane

@@

majority of 2D nonmetals, the off-diagonal elements of the

@@

\varepsilon_{\mathrm{SL}}^{zz}$. 
The absence of bonding perpendicular
to the plane confines the induced dipoles along the
\textit{z}-direction as the charge density difference, $\Delta \rho=\rho(\boldsymbol{E}) - \rho(0)$,
at zero and finite electric fields ($|\boldsymbol{E}_{}|=0.01 \mathrm{V\cdot \AA}^{-1}$) 
extends to $\sim{}$12 \AA{} deeply into the vacuum (Figure \ref{fig-1}{\bf a}). When $L$ is large enough,   
the induced dipoles $\boldsymbol{u}$ from the periodic images do not interact mutually 
as the integral in Eq. \ref{eq:def-eps-2} depends only locally on the atomic charge density at the layer. 
However, we can see from Eqs. \ref{eq:def-eps-1} that both

@@

$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on $L$ via the volume of the cell $\Omega$. 
Therefore, any calculation performed using such definition will intrinsically depend on the magnitude of $L$ as an additional parameter. 
This dependence can be clearly demonstrated by

@@

theory (DFT) using hybrid functionals (see {\it Methods} for details) as a function 
of $L$ for P$\bar{6}$m2 transitional metal dichalcogenides 
(TMDCs), 2H-MX$_{2}$, where M=Mo, W and X=S, Se,
Te (top panels of Figure \ref{fig-1}{\bf b} and \ref{fig-1}{\bf c}, respectively). 
Despite of the magnitudes of $L$ both components of the dielectric constant 
change systematically without a clear convergence.  
%
Simulations performed at higher levels of theory using 
many-body techniques, G$_{\rm 0}$W$_{0}$ (Supplementary Figure \ref{fig:S1}), 
and also taking into account  electron-hole excitations at the level of the Bethe-Salpeter equation 
at the frequency-dependent versions of $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$
invariably give alike results (Supplementary Figure \ref{fig:S2}). 
Indeed, the variations observed in peak positions at different values of $\omega(eV)$ 
implicate that several other related quantities, such as, the optical absorption and 
optical conductivity, suffer the same deficiencies. In a fully first-principles theory 
such intrinsic dependence on $L$ should not be present. 
%
%
%
%as the computation of the dielectric function is based on alike formalism\cite{Ehrenreich-Cohen paper}
% We can understand this behavior in terms of the electrostatic of the problem. 
%
%
%
%This result indicates that the use of the dielectric constant to represent 
%dielectric properties at the static limit of a 2D material is 
%ambiguous as the long-range correlations between the layers would only 
%be negligible at the limit of $L \rightarrow \infty$, which incidentally modify the magnitudes of 
%$\varepsilon^{\parallel, \perp}_{\mathrm{SL}}$ in the convergence. 
%
It is worth mentioning that experimental results also need to define an effective thickness of the sheet 
to interpret ellipsometry data \cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, 
reflectance or transmission spectra \cite{Li_2014, Yoffe-Wilson69} in 
order to extract information for the real part of the dielectric functions. 
We argue that such procedure may induce inevitably variations of the results as the 
thickness is normally chosen by the interlayer spacing of the 
respective bulk materials (Supplementary Section \ref{sec:2D-3D-rescale} gives an exhaustive analysis).  
%
%%%
%

@@

%.
%
%
%As a result, the $L$-dependency of $\varepsilon_{\mathrm{SL}}$ makes
%it impractical to represent the dielectric nature of a 2D material
%both theoretically and experimentally, because the size of vacuum
%layer must always be considered. 
%

To solve this problem, we need to
find the $L$-independent alternative of
$\varepsilon_{\mathrm{SL}}$. As described before, by multiplying
Eq. \ref{eq:def-eps-2} with $L$ we obtain the sheet polarization density
$\boldsymbol{\mu}_{\mathrm{2D}}$, that is, 
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, 
which is independent of $L$ due to the locality 
of $\boldsymbol{u}$ and $A$. 
%
Similar to the definition of molecular
polarizability \cite{Israelachvili_2011},
$\boldsymbol{\mu}_{\mathrm{2D}}$ is associated with the 2D
polarizability $\alpha_{\mathrm{2D}}$ through:
$\boldsymbol{\mu}^{p} = \sum_{q} \alpha_{\mathrm{2D}}^{pq}
\boldsymbol{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where
$\boldsymbol{E}_{\mathrm{loc}}$ is the local electric field. 
Using electrostatic boundary conditions, 
the continuity of the electric field along the
in-plane direction gives
$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$
\cite{Markel_2016}. For the out-of-plane component, the dipole
screening yields
$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}_{\mathrm{2D}}^{\perp}/L$
\cite{Meyer_2001_dipole_slab,T_bik_2004}. Combining with
Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we can relate the 2D polarizabilities,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:
%
%
\begin{subequations}
\begin{eqnarray}
  \label{eq:alpha-para-def}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0}L}\\
  \label{eq:alpha-perp-def}
  &\varepsilon_{\mathrm{SL}}^{\perp} &= \left(1 - {\displaystyle \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{\mathrm{0}} L}} \right)^{-1}
\end{eqnarray}
\end{subequations}
%
%
The bottom panels of Figure \ref{fig-1}b and \ref{fig-1}c show the
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the selected TMDCs as a function of $L$, calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}. We observe
that both $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ reached 
convergence in a much shorter vacuum length within 10 \AA ~and 15 \AA, respectively. 
%
%
Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} 
to reproduce the trends noticed in the top panels in Fig.\ref{fig-1}{\bf b} and \ref{fig-1}{\bf c}  
for $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around 
a centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ 
and $\alpha_{\mathrm{2D}}^{\perp}$ (Fig. \ref{fig-1}{\bf d-e}). 
A similar curve profile is obtained in both components of the dielectric constant including the much 
abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
interlayer interactions.  Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can also be used to remove 
the dependence of $L$ on $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ via $\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$, respectively (Supplementary Figure \ref{fig:S3}). 
%
% 
% 
% 
% 
These findings provide that the 2D polarizability captures the essence of the dielectric properties 
of layered materials as the microscopic quantity in describing the 
atomic interactions present in the layers. Its local nature removes any dependence on size effects 
present in the calculations.  
More discussions about the choice of the 2D polarizability
and comparison with other methods can be found in Supplementary Section \ref{sec:2D-3D-rescale}.

%\subsection*{Polarizability as the fundamental variable}
%\label{sec:first-principles}

%We consider

As a consequence of Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, we can demonstrate 
that other quantities are intrinsically related to the polarizability. 
Using random phase approximation (RPA)
theory \cite{Adler_1962} within the $\mathbf{k} \cdot \mathbf{p}$
formalism\cite{kittel_2005_introduction} (see Supplementary
Section \ref{sssec:theory-1} and  \ref{ssec:theory-2} for details), 
we can show that
can be written as: 
%
%
%

@@

\label{eq:2D-Moss-para}
  &\alpha_{\mathrm{2D}}^{\parallel} &=C^{\parallel} E_{g}^{-1} \\
  \label{eq:2D-Moss-perp}
  &\alpha_{\mathrm{2D}}^{\perp} & =C^{\perp} \delta

@@

%
%
%
%
where $E_{\mathrm{g}}$ is the minimal electronic bandgap, 
$\delta$ is the intrinsic or covalent thickness of the layer (Fig. \ref{fig-1}{\bf a}), and $C^{\parallel} = {8\pi^{2}\varepsilon_0\AA}/{eN}$, where $N$ corresponds to the degeneracy of the bands associated with $E_{\mathrm{g}}$,
and $C^{\perp} = {1}/{4\pi}$.  Despite of the simplicity of Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}, 
they generalize a direct relationship between the polarizability and the electronic and structural properties for any 
2D material in a new framework. 
We can show that these equations are valid for the current library of known layered materials 
involving different lattice symmetry, element composition, optical and electronic properties. 
%
A high-throughput screening performed on 
different families of TMDCs (MX\(_{\text{2}}\), where M is
a metal in groups 4, 6, 10, and X=O, S, Se, Te) and phases (P\(\bar{6}\)m2, P3m1), 
metal monochalcogenides
(Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
I), hexagonal boron nitride (BN), graphene derivatives (fluorographene
(C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)), phosphorene (P$_{4}$)
and thin layer organic-inorganic perovskites (ABX$_{3}$) (Fig. \ref{fig-3}{\bf a}) 
showed that our method enables full correlation between these disparate variables. 
%%
%
%Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are the main conclusions of this work. 
%
% \todo[inline]{I not sure if we need to show the proportional coefficients
%  here. $\alpha_{2D}^{\perp}$ is almost certain to be
%  $\varepsilon_{0}\delta$, but $\alpha_{\mathrm{2D}}^{\parallel}$ has
%  a more complex coefficient.}
%
%
%
%The static 2D
%polarizabilities are calculated from the static dielectric response of
%the selected 2D materials (see {\it Methods}). 
Figure \ref{fig-3}{\bf b}
shows the calculated $E_{\mathrm{g}}$ (blue dots) and polarizabilities
(bar plots) of all the 2D materials investigated, covering a wide
spectrum range from far-infrared to ultraviolet at HSE06 level. 
Note from dimension
analysis, it is more intuitive to express the polarizability as
$\alpha_{\mathrm{2D}}/(4 \pi \varepsilon_{0})$, which has unit of
\AA. We find that $\alpha_{\mathrm{2D}}^{\parallel}$ has a general
descending trend when $E_{\mathrm{g}}$ increases, while 
no apparent correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and
$E_{\mathrm{g}}$ is observed (see Supplementary Section
\ref{sec:pol-2D-Eg}). It is worth mentioning that materials with elements 
having large polarizabilities, such as Hf and Zr in 1T-HfO$_2$ or 1T-ZrO$_2$, 
respectively, also transfer alike features for the layers with slightly variations between 
1T and 2H phases. The former normally shows larger values of $\alpha_{\mathrm{2D}}^{\parallel}$ 
than the latter. 
%
% 
We then examine Eqs. \ref{eq:2D-Moss-para}
and \ref{eq:2D-Moss-perp} using the polarizabilities calculated by
first-principle calculations. 
Figure \ref{fig-3}{\bf c} shows
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
\AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D
materials investigated (circle dots).  
A linear regression coefficient of $R^{2}=0.84$ indicates a 
strong correlation between bandgaps and polarizabilities as predicted in 
Eq. \ref{eq:2D-Moss-para}. 
We also discover that
the linearity between
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$ (measured by the $R^{2}$ value) is higher when the
bandgap is calculated using the HSE06 hybrid functional\cite{Heyd_2005} compared
with that from Perdew--Burk--Ernzerhof (PBE) %exchange correlation functional
(see Supplementary Section \ref{sec:pol-2D-Eg} and
Supplementary Figure \ref{fig:alpha-Eg-diff}) which suggests that higher levels 
of theory are needed to predict bandgaps as it is normally the case.   
We also show
that the proposed Eq. \ref{eq:2D-Moss-para}
behaves equivalently well when using the
experimentally accessible optical bandgap of 2D materials (details see
Supplementary Section \ref{sec:gpaw-2} and Supplementary Figure
\ref{fig:opt}).
